### 2018-08-09 paper/approach.tex
Changes some Sphinx to \ac{Sphinx}

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from Sphinx and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as Sphinx, unidirectional (network structure), 
message-based (performance) communication.
But unlike Sphinx, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

\Sphinxes does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as Sphinx, it can be used in many different settings.

>>>>

As depicted in Figure~\ref{fig:outline}, \ac{SPORES} relies on a predictive and probabilistic onion routing protocol (\ac{SPOR}). \ac{SPOR} in turn combines a multi-set mix-header format (\Sphinxes) together with a node selection protocol that exploits decentralized prediction regarding node availability to optimize the reliability of \Sphinxes without jeopardizing its security properties.
%% Particularly, \sphinxes (\cref{Sphinxes}), is an adaptation of the 
%% \sonja{do we apply all categories here?} \ac{Sphinx} mix-header format.
%% This means that we inherit some properties from \ac{Sphinx} and due to being only a 
%% header format, it only imposes some restrictions in the above categories.
\Sphinxes (Figure~\ref{fig:outline} \ding{202}) provides, just as \ac{Sphinx}, unidirectional (network structure), 
message-based (performance) communication.
But unlike \ac{Sphinx}, \Sphinxes is an hybrid source-hop-by-hop routed, and a
source-bounded random walk (communication 
model). \Sphinxes relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
\Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set just as she can learn the single node constituting a layer of a
secure onion-routing scheme without endangering the security
properties~\cite{CLOnionRouting}).

\Sphinxes does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in \ac{Tor}) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as \ac{Sphinx}, it can be used in many different settings.

### 2018-08-09 paper/sphinxes.tex
Changes some Sphinx to \ac{Sphinx}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
Sphinx only provides one node per onion layer; in this section we extend Sphinx 
to \Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

@@

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

The Sphinx header (for the first node) is a triple \((\alpha_1, \beta_1, 
  \gamma_1)\), where \(\alpha_1\) is \iac{DHKE} exponent (\(g^x\), where \(x\) 
is a short-term secret chosen randomly for each header), \(\beta_1\) is the 
encrypted routing data and \(\gamma_1\) is \iac{MAC} for \(\beta_1\).
The payload data, \(\delta\), is treated separately from the header.

@@

We will now extend Sphinx to do \ac{SPOR}: instead of providing only \(d_{i+1}\) 
in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
of \(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

In Sphinx, the public key for layer \(i\) is denoted as \(\pk_i\).
Since we have \(m\) alternative nodes with different keys, let us denote them 
by \(\pk_i^{(1)}, \dotsc, \pk_i^{(m)}\).

@@

We keep the nomenclature of mix headers and messages from Sphinx for
clarity but later apply them to onions and file chunks, repectively.

@@

This algorithm creates a header for \iac{SPOR}.
It is identical to that of Sphinx~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.

>>>>

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security. \sonja{what about the CL properties?}
Sphinx only provides one node per onion layer; in this section we extend \ac{Sphinx} 
to \Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
% AL: Bounded random-walk....
As such, \Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

@@

We will now give an overview of the \ac{Sphinx} header format.
The idea is not to give a detailed description of \ac{Sphinx}, but to give the 
reader enough understanding of \ac{Sphinx} to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

The \ac{Sphinx} header (for the first node) is a triple \((\alpha_1, \beta_1, 
  \gamma_1)\), where \(\alpha_1\) is \iac{DHKE} exponent (\(g^x\), where \(x\) 
is a short-term secret chosen randomly for each header), \(\beta_1\) is the 
encrypted routing data and \(\gamma_1\) is \iac{MAC} for \(\beta_1\).
The payload data, \(\delta\), is treated separately from the header.

@@

We will now extend \ac{Sphinx} to do \ac{SPOR}: instead of providing only \(d_{i+1}\) 
in \(\beta_i\), we will have a set \(\{d_{i+1}^{(1)}, \dotsc, d_{i+1}^{(m)}\}\) 
of \(m\) alternative next nodes.
This means that all \(m\) nodes must be able to compute the same shared secret 
\(s_{i+1}\).
We do this by adding one layer of indirection.

In \ac{Sphinx}, the public key for layer \(i\) is denoted as \(\pk_i\).
Since we have \(m\) alternative nodes with different keys, let us denote them 
by \(\pk_i^{(1)}, \dotsc, \pk_i^{(m)}\).

@@

We keep the nomenclature of mix headers and messages from \ac{Sphinx} for
clarity but later apply them to onions and file chunks, repectively.

@@

This algorithm creates a header for \iac{SPOR}.
It is identical to that of \ac{Sphinx}~\cite[\S 3.2]{Sphinx} except that we use a 
set of addresses and keys for each layer instead of only one address and key.
Also, we do not distinguish between addresses of destinations and routers.
